### 2020-02-12 paper5/article.tex
DLCD -> HLGD. Re-read Chp 2,3. Briefly paper 7.

\section{Introduction} \label{sec:introduction}
The understanding of liquid-liquid emulsions is important in many industrial processes \eg hydrocarbon separation, suspension crystallization, and emulsion polymerization. These flows are characterized by density and viscosity ratios on the order of unity (\eg water and oil mixtures) and a source of agitation (\eg an impeller) that creates a turbulent two-phase mixture consisting of a dispersed phase of droplets and a continuous phase. The resulting turbulence in the carrier phase is altered directly by the droplet feedback on the surrounding fluid and indirectly by droplet-droplet interactions. Many aspects of the complex interaction of the dispersed phase with the continuous phase are not well understood. In particular, there are questions related to the topological changes and to the role of the surface tension of the dispersed phase, the stationarity of the turbulent statistics, and the kinetic energy budget.

@@

\subsection{Setup}
The problem is governed by several dimensionless parameters, which define the problem under consideration. First, the computational box is defined by two aspect ratios $\AR_{xz} = L_x/L_z$ and $\AR_{yz} = L_y/L_z$ which are fixed equal to $2.05$ and $1.025$ respectively. These values have been chosen accordingly to what proposed by \cite{sekimoto_dong_jimenez_2016a} as ``acceptable" in the sense that they fall within the range of parameters in which the flow is as free as possible from box effects and can thus be used as a model of shear-driven turbulence in general. Indeed, homogeneous shear turbulence in an infinite domain evolves towards larger and larger length scales while simulations in a finite box are necessarily constrained to some degree by the box geometry. These authors noticed that the effect of the geometry can be reduced by ensuring that $L_z$ is the main constraint, thus resulting in the flow being ``minimal" in the spanwise direction. Next, once the size of the numerical box is fixed, to fully characterize the problem we define the shear Reynolds number based on the box width
\begin{equation}
Re_z = \frac{\mathcal{S} L_z^2}{\nu},
\end{equation}
the Weber number based on the initial droplet diameter $D_0$
\begin{equation}
\label{eq:wes}
We_{\mathcal{S}_0} = \frac{\rho \mathcal{S}^2 D_0^3}{\sigma},
\end{equation}
and the ratio of the initial droplet diameter to the box size $\AR_{Dz}=D_0/L_z$. In the following, we consider one case of single-phase flow as reference and nine cases of two-phase flows, all at the same Reynolds number equal to $15200$; in the multiphase cases, we vary the ratio $\AR_{Dz}$ and $We_{\mathcal{S}_0}$, as summarized in \tabref{tab:cases}. Note that, the Weber number here is mainly determined by the interfacial surface tension $\sigma$. Two other nondimensional parameters are the density and viscosity ratios, which are fixed to unity to study the individual effect of the Weber number (interfacial surface tension).

Besides the parameters just defined and based on the geometrical dimensions and initial and boundary conditions alone, in the following discussion we will use other nondimensional numbers because they turned out to be more relevant to understand the problem at hand; in particular, the two non-dimensional parameters which characterize the single-phase homogeneous shear turbulent flows, the Taylor-microscale Reynolds number $Re_\lambda$ and the shear-rate parameter $S^*$, defined as
\begin{equation}
\label{eq:rel}
Re_\lambda = \left( \frac{2\mathcal{K} }{3} \right)^{1/2} \frac{\lambda}{\nu} = \left( \frac{5}{3 \nu \varepsilon } \right)^{1/2} 2\mathcal{K},
\end{equation}
and
\begin{equation}
\label{eq:ss}
S^* = \frac{2 \mathcal{S} \mathcal{K} }{\varepsilon},
\end{equation}
where $\lambda = \sqrt{10\nu \mathcal{K}/\varepsilon}$ is the Taylor microscale \citep{sekimoto_dong_jimenez_2016a}, $\mathcal{K} = \langle \rho u'_i u'_i \rangle/2$ is the turbulent kinetic energy per unit volume, and $\varepsilon = \mu \langle \partial u'_i/\partial x_j : \partial u'_i/\partial x_j \rangle$ is the dissipation rate of the fluctuating energy. These two non-dimensional numbers can be interpreted as the ratio of the eddy-turnover time $\tau_0= \left( 2\mathcal{K} \right)^{1/2}/\varepsilon$ and the Kolmogorov time scale $\tau_K= \left( \nu / \varepsilon \right)^{1/2}$ and the mean shear time scale $\tau_\mathcal{S} = 1/ \mathcal{S}$, respectively.

\begin{figure}
	\centering
	\input{paper5/WeSrms} \vspace{0.5cm}
	\caption{The ratio of the two Weber numbers introduced here, one based on the mean shear $We_{\mathcal{S}_0}$ and one on the velocity fluctuations $We_{\textrm{rms}_0}$, as a function of the Weber number based on the initial droplet size, $We_0$. The circle, square and triangle symbols are used to distinguish cases with different surface tension but same ratio $We_{\mathcal{S}_0}/We_{\textrm{rms}_0}$, while the brown, green and blue colors represent cases with the ratio $We_{\mathcal{S}_0}/We_{{rms}_0}$ equal to $1/5$, $1$ and $5$, respectively. These symbols and color scheme will be used throughout the rest of the paper.}
	\label{fig:Web}
\end{figure}
Weber numbers can be defined in several ways. In \equref{eq:wes} we defined the Weber number based on the mean shear, but it can also be defined based on the velocity fluctuations, thus obtaining
\begin{equation}
\label{eq:werms}
We_{\textrm{rms}_0} = \frac{2 \rho \mathcal{K} D_0}{\sigma}.
\end{equation}
Note that, the latter definition is the one usually used in homogeneous isotropic turbulent flows in the absence of a mean flow \citep{dodd_ferrante_2016a}. Both the Weber numbers $We_{\mathcal{S}_0}$ and $We_{\textrm{rms}_0}$ are of interest since they are based on two different mechanisms that may affect the droplets dynamics: on large scales (large droplets) the effect of the mean shear is dominant, while on small scales (small droplets) the flow is mainly dominated by the isotropic turbulent fluctuations. Our set of parameters is chosen such that the ratio of these two Weber numbers $We_{\mathcal{S}_0}/We_{{rms}_0}$ equals $1/5$, $1$ and $5$, as reported in \figrefS{fig:Web}. In general both the mechanisms are present together and hence we can define a Weber number which incorporates both the effects as
\begin{equation}
\label{eq:we0}
We_0 = \frac{\rho \left( \sqrt{2\mathcal{K}} + \mathcal{S} D_0 \right)^2 D_0}{\sigma}.
\end{equation}
Finally, we can define a Weber number based on $\lambda$ as
\begin{equation}
\label{eq:wel}
We_\lambda = \frac{\rho \left( \sqrt{2\mathcal{K}} + \mathcal{S} \lambda \right)^2 \lambda}{\sigma}.
\end{equation}
The choice of using $\lambda$ in the definition of the Weber number instead of a dimension associated to the suspended phase is due to the fact that the interface is not only deforming, thus losing its original spherical shape, but also actively undergoing merging and break-up processes, which makes the definition of a unique dimension difficult. Therefore, we propose to rely on a fluid length scale, which, as shown below in the results, yields a good collapse of our data. In the following discussion, we use $We_\lambda$ to discuss the results; the value of $We_0$ is reported in order to fully characterize the initial conditions of the present simulations.

\subsection{Code validation}
The numerical code used in this work has been extensively validated in the past for multiphase turbulent flows simulations \citep{rosti_brandt_2017a, rosti_banaei_brandt_mazzino_2018a, rosti_izbassarov_tammisola_hormozi_brandt_2018a}. Here, we provide one more comparison with literature results for the specific case of HST.
\begin{figure}
	\centering
	\input{paper5/pumir} \hspace{0.5cm}
	\input{paper5/pumirpdf} \vspace{0.5cm}
\caption{(a) Time history of the turbulent kinetic energy $\mathcal{K}=\langle u'_i u'_i \rangle/2$ (black line) and enstrophy $\Omega$ (grey line), normalized by their mean values. (b) Normalized histogram of the streamwise (red) and shear (orange) components of the velocity fluctuations, $u'$ and $v'$. The lines and symbols are used to distinguish our results (lines) from those by \citet{pumir_1996a}.}
	\label{fig:pumir}
\end{figure}
The single-phase homogeneous shear turbulence has been validated by reproducing one of the cases investigated by \citet{pumir_1996a}; in particular, we simulated the Run No.~$2$ in that paper. The initial condition at $t = 0$ is a homogeneous isotropic turbulent field at $Re_\lambda = 50.8$, obtained in a square computational box of size $2\pi$ discretised with $256$ grid points in each direction. From the time history of the turbulent kinetic energy $\mathcal{K}$ and of the enstrophy $\Omega = \langle \omega_i \omega_i \rangle$, shown in \figref[a]{fig:pumir}, we observe a first transient phase for $0 \le t\mathcal{S} \le 30$, where the kinetic energy and enstrophy grow rapidly, followed by a statistically stationary state characterized by a cyclic succession of turbulent kinetic energy peaks rapidly followed by a peak in enstrophy with a time lag of approximately $5\mathcal{S}$. This behavior is well captured in our simulation. A quantitative validation is performed first by comparing the mean components of the velocity anisotropy tensor, $b_{ij}=\langle u_i u_j / u'_k u'_k - \delta_{ij}/3 \rangle$ computed in our simulations ($b_{11}=0.231$, $b_{22} = −0.129$, $b_{33} = −0.101$, $b_{12} = −0.147$) with the data reported by \citet{pumir_1996a}, and we found that the differences are below $5\%$. A further comparison is shown in \figref[b]{fig:pumir} where the normalized histograms of the streamwise and shear components of the velocity obtained with the present  simulations are compared with the results reported in the literature \citep{pumir_1996a}; again we observe a very good agreement.

@@

We start our analysis by considering the single-phase flow at $Re_z = 15200$. The problem is solved numerically on a computational mesh of $1312 \times 640 \times 624$ grid points and the simulation is run for approximately $250\mathcal{S}$ time units. Note that, the grid spacing is chosen sufficiently small for good resolution of the smallest turbulent scales as indicated by $\Delta x / \eta \approx 0.7$, where $\eta$ is the Kolmogorov scale defined as $\eta=\left( \mu/\rho \right)^{3/4}/\varepsilon^{1/4}$. The initial flow field is  fully developed single-phase homogeneous isotropic turbulence, and the mean shear $\mathcal{S}$ is applied from $t=0$. As shown in \figref[a]{fig:kin}, once the shear is applied, the flow undergoes an initial transient characterized by a strong increase in the production of turbulent kinetic energy, which is not in balance with the dissipation rate. After some time, however, the turbulent kinetic energy $\mathcal{K}$ decreases owing to an increase in the dissipation, reaching a new statistically steady state where, on average, the production balances the dissipation ($\mathcal{P} \approx \varepsilon$). This state, called steady-state shear turbulence, was first found and characterized by \cite{pumir_1996a} and later investigated by others \citep[e.g.][]{sekimoto_dong_jimenez_2016a}. The resulting Taylor microscale Reynolds number at the steady state is equal to $Re_\lambda \approx 145$ with the averaged spectrum of the TKE reported in \figref[b]{fig:kin}. Owing to the high Reynolds number, a clear $k^{-5/3}$ regime develops at intermediate scales. We also observe that the spectra of each individual component of the velocity are different at small wave numbers because of the large-scale anisotropy, while all spectra coincide at higher wave numbers, consistently with what observed by \cite{pumir_1996a}.

@@

\subsection{Size distribution}
We now study the transient and steady state property of the interface separating the two fluids. \figrefSC{fig:3dview} shows instantaneous snapshots of the two-phase flow at the statistically steady state, which is characterized by droplets with different sizes and shapes: in general we can observe that small droplets are approximately spherical, while the largest ones have very anisotropic shapes and show a preferential alignment with the direction of the mean shear. Also, as the Weber number decreases, the droplets size increases and larger droplets can sustain the spherical shape.

@@

\begin{figure}
	\centering
	\input{paper5/Cvol} \vspace{0.5cm} \\
\includegraphics[width=0.49\textwidth]{contL}
\put(-190,130){$(b)$}
\includegraphics[width=0.49\textwidth]{contR}
\put(-190,130){$(c)$}
	\caption{(a) Normalized cumulative volume distributions $\mathcal{V}/\mathcal{V}_\textrm{tot}$ of the dispersed phase at the steady state as a function of the equivalent spherical droplet diameters $D$. The horizontal grey line correspond to the level $\mathcal{V}=0.95\mathcal{V}_\textrm{tot}$. (b-c) Contour of the temporal evolution of the normalized cumulative volume distributions of the dispersed phase as a function  of the equivalent spherical droplet diameter for cases $4$ (b) and $5$ (c).}
	\label{fig:distr}
\end{figure}
Next, we aim to characterize the steady state size distribution of the emulsion. Thus, we first examine the cumulative volume, $\mathcal{V}$, as a function of the equivalent spherical diameter $D$ defined as the diameter of the sphere occupying the same volume, see \figref[a]{fig:distr}. Specifically, \figref[a]{fig:distr} shows the steady-state distributions of all cases, where each point on the curves represents the total volume of the droplets with equivalent diameter lower than $D$. In the figure, both $\mathcal{V}$ and $D$ are normalized by the global maximal values so that the curves are bounded uniformly from above by $1$. The figure shows that the cumulative volume distribution only has one inflection point ($d^2 \mathcal{V}/dD^2 = 0$), thus indicating that the probability density plot ($d \mathcal{V}/dD$) is single peaked. In \figref[a]{fig:distr} the Weber number $We_\lambda$ grows from right to left, as indicated by the list of symbols, suggesting that small droplets tend to be more common at high Weber numbers. Additionally, the range of the droplet diameters also narrows with increasing $We_\lambda$, since the cumulative volume grows faster to unity, as visually confirmed in \figrefS{fig:3dview}. Case $2$, blue line with circle, is the only simulation exhibiting a double peak (\ie $d \mathcal{V}/dD$ has two local maxima): this is due to the presence of very small droplets together with few large ones as can be seen in \figref[left]{fig:3dview}. Nevertheless, the overall trend of decreasing size for increasing Weber number is still consistent with the linear scaling between $\mathcal{N}_s$ and $We_\lambda$, as already observed in \figref[b]{fig:count}. The two bottom panels in \figrefS{fig:distr}, are contours of $\mathcal{V}/\mathcal{V}_\textrm{tot}$ as a function of the equivalent diameter $D$ and time, and can thus be interpreted as a cumulative spectrogram with most of the droplets centered in the region where the gradient of the color is the largest. In particular, we selected two specific cases, with same initial Weber number $We_0 \approx 2$, but different initial droplet size and surface tension, thus leading to different $We_\lambda$. The two figures show the transient behavior for cases $4$ and $5$, respectively: in \figref[b]{fig:distr} the mean size distribution remains relatively unchanged over time but it is subject to strong fluctuations, while \figref[c]{fig:distr} shows a clear shift of the population from large droplets to small ones, with a statistically steady state characterized by small fluctuations.

@@

\begin{figure}
	\centering
	\input{paper5/surf} \vspace{0.5cm}
	\caption{Total interfacial area $\mathcal{A}$ as a function of the Weber number $We_\lambda$. The grey solid line is a fit to our data in the form of $\mathcal{A} \propto We_\lambda^{1/3}$.}
	\label{fig:surf}
\end{figure}
Finally, we can further characterize the size distribution of the emulsion by inspecting the total surface area $\mathcal{A}$ of the dispersed phase. This quantity is very important when studying multiphase flows with interfaces, since the rate of work due to the surface tension is equal to the product of the surface tension coefficient and the rate of change in interfacial surface area \citep{dodd_ferrante_2016a}; also, for many industrial applications, the total surface area is often the most important parameter as surfactants tend to reside on the interface or it determines the chemical reaction rate. \figrefSC{fig:surf} reports the steady state surface area $\mathcal{A}$ as a function of the Weber number $We_\lambda$ and clearly shows that the surface area increases monotonically with the Weber number. As we have shown above that $\mathcal{N} \propto We_\lambda$, combining with mass conservation, \ie $\mathcal{N} D^3 \propto 1$, leads to the following relation for the total area: $\mathcal{A} \propto \mathcal{N} D^2 \propto We_\lambda^{1/3}$. In other words, the surface area of the droplets shall also increase with the Weber number defined by the Taylor length of the flow, with a slope of $1/3$. \figrefSC{fig:surf} verifies this scaling. We remark that in the derivation above, we have assumed that the droplets are spherical, which is not always true in our cases. However, provided the linear scaling between $\mathcal{N}$ and $We_\lambda$ remains valid, we expect the $1/3$ scaling law to hold for a wide range of emulsions.

>>>>

\section{Introduction} \label{sec:introduction}
The understanding of liquid-liquid emulsions is important in many industrial processes \eg hydrocarbon separation, suspension crystallization, and emulsion polymerization. These flows are characterised by density and viscosity ratios on the order of unity (\eg water and oil mixtures) and a source of agitation (\eg an impeller) that creates a turbulent two-phase mixture consisting of a dispersed phase of droplets and a continuous phase. The resulting turbulence in the carrier phase is altered directly by the droplet feedback on the surrounding fluid and indirectly by droplet-droplet interactions. Many aspects of the complex interaction of the dispersed phase with the continuous phase are not well understood. In particular, there are questions related to the topological changes and to the role of the surface tension of the dispersed phase, the stationarity of the turbulent statistics, and the kinetic energy budget.

@@

\subsection{Setup}
The problem is governed by several dimensionless parameters, which define the problem under consideration. First, the computational box is defined by two aspect ratios $\AR_{xz} = L_x/L_z$ and $\AR_{yz} = L_y/L_z$ which are fixed equal to $2.05$ and $1.025$ respectively. These values have been chosen accordingly to what proposed by \cite{sekimoto_dong_jimenez_2016a} as ``acceptable" in the sense that they fall within the range of parameters in which the flow is as free as possible from box effects and can thus be used as a model of shear-driven turbulence in general. Indeed, homogeneous shear turbulence in an infinite domain evolves towards larger and larger length scales while simulations in a finite box are necessarily constrained to some degree by the box geometry. These authors noticed that the effect of the geometry can be reduced by ensuring that $L_z$ is the main constraint, thus resulting in the flow being ``minimal" in the spanwise direction. Next, once the size of the numerical box is fixed, to fully characterise the problem we define the shear Reynolds number based on the box width
\begin{equation}
Re_z = \frac{\mathcal{S} L_z^2}{\nu},
\end{equation}
the Weber number based on the initial droplet diameter $D_0$
\begin{equation}
\label{eq:wes}
We_{\mathcal{S}_0} = \frac{\rho \mathcal{S}^2 D_0^3}{\sigma},
\end{equation}
and the ratio of the initial droplet diameter to the box size $\AR_{Dz}=D_0/L_z$. In the following, we consider one case of single-phase flow as reference and nine cases of two-phase flows, all at the same Reynolds number equal to $15200$; in the multiphase cases, we vary the ratio $\AR_{Dz}$ and $We_{\mathcal{S}_0}$, as summarized in \tabref{tab:cases}. Note that, the Weber number here is mainly determined by the interfacial surface tension $\sigma$. Two other nondimensional parameters are the density and viscosity ratios, which are fixed to unity to study the individual effect of the Weber number (interfacial surface tension).

Besides the parameters just defined and based on the geometrical dimensions and initial and boundary conditions alone, in the following discussion we will use other nondimensional numbers because they turned out to be more relevant to understand the problem at hand; in particular, the two non-dimensional parameters which characterise the single-phase homogeneous shear turbulent flows, the Taylor-microscale Reynolds number $Re_\lambda$ and the shear-rate parameter $S^*$, defined as
\begin{equation}
\label{eq:rel}
Re_\lambda = \left( \frac{2\mathcal{K} }{3} \right)^{1/2} \frac{\lambda}{\nu} = \left( \frac{5}{3 \nu \varepsilon } \right)^{1/2} 2\mathcal{K},
\end{equation}
and
\begin{equation}
\label{eq:ss}
S^* = \frac{2 \mathcal{S} \mathcal{K} }{\varepsilon},
\end{equation}
where $\lambda = \sqrt{10\nu \mathcal{K}/\varepsilon}$ is the Taylor microscale \citep{sekimoto_dong_jimenez_2016a}, $\mathcal{K} = \langle \rho u'_i u'_i \rangle/2$ is the turbulent kinetic energy per unit volume, and $\varepsilon = \mu \langle \partial u'_i/\partial x_j : \partial u'_i/\partial x_j \rangle$ is the dissipation rate of the fluctuating energy. These two non-dimensional numbers can be interpreted as the ratio of the eddy-turnover time $\tau_0= \left( 2\mathcal{K} \right)^{1/2}/\varepsilon$ and the Kolmogorov time scale $\tau_K= \left( \nu / \varepsilon \right)^{1/2}$ and the mean shear time scale $\tau_\mathcal{S} = 1/ \mathcal{S}$, respectively.

\begin{figure}
	\centering
	\input{paper5/WeSrms} \vspace{0.5cm}
	\caption{The ratio of the two Weber numbers introduced here, one based on the mean shear $We_{\mathcal{S}_0}$ and one on the velocity fluctuations $We_{\textrm{rms}_0}$, as a function of the Weber number based on the initial droplet size, $We_0$. The circle, square and triangle symbols are used to distinguish cases with different surface tension but same ratio $We_{\mathcal{S}_0}/We_{\textrm{rms}_0}$, while the brown, green and blue colors represent cases with the ratio $We_{\mathcal{S}_0}/We_{{rms}_0}$ equal to $1/5$, $1$ and $5$, respectively. These symbols and color scheme will be used throughout the rest of the paper.}
	\label{fig:Web}
\end{figure}
Weber numbers can be defined in several ways. In \equref{eq:wes} we defined the Weber number based on the mean shear, but it can also be defined based on the velocity fluctuations, thus obtaining
\begin{equation}
\label{eq:werms}
We_{\textrm{rms}_0} = \frac{2 \rho \mathcal{K} D_0}{\sigma}.
\end{equation}
Note that, the latter definition is the one usually used in homogeneous isotropic turbulent flows in the absence of a mean flow \citep{dodd_ferrante_2016a}. Both the Weber numbers $We_{\mathcal{S}_0}$ and $We_{\textrm{rms}_0}$ are of interest since they are based on two different mechanisms that may affect the droplets dynamics: on large scales (large droplets) the effect of the mean shear is dominant, while on small scales (small droplets) the flow is mainly dominated by the isotropic turbulent fluctuations. Our set of parameters is chosen such that the ratio of these two Weber numbers $We_{\mathcal{S}_0}/We_{{rms}_0}$ equals $1/5$, $1$ and $5$, as reported in \figrefS{fig:Web}. In general both the mechanisms are present together and hence we can define a Weber number which incorporates both the effects as
\begin{equation}
\label{eq:we0}
We_0 = \frac{\rho \left( \sqrt{2\mathcal{K}} + \mathcal{S} D_0 \right)^2 D_0}{\sigma}.
\end{equation}
Finally, we can define a Weber number based on $\lambda$ as
\begin{equation}
\label{eq:wel}
We_\lambda = \frac{\rho \left( \sqrt{2\mathcal{K}} + \mathcal{S} \lambda \right)^2 \lambda}{\sigma}.
\end{equation}
The choice of using $\lambda$ in the definition of the Weber number instead of a dimension associated to the suspended phase is due to the fact that the interface is not only deforming, thus losing its original spherical shape, but also actively undergoing merging and break-up processes, which makes the definition of a unique dimension difficult. Therefore, we propose to rely on a fluid length scale, which, as shown below in the results, yields a good collapse of our data. In the following discussion, we use $We_\lambda$ to discuss the results; the value of $We_0$ is reported in order to fully characterise the initial conditions of the present simulations.

\subsection{Code validation}
The numerical code used in this work has been extensively validated in the past for multiphase turbulent flows simulations \citep{rosti_brandt_2017a, rosti_banaei_brandt_mazzino_2018a, rosti_izbassarov_tammisola_hormozi_brandt_2018a}. Here, we provide one more comparison with literature results for the specific case of HST.
\begin{figure}
	\centering
	\input{paper5/pumir} \hspace{0.5cm}
	\input{paper5/pumirpdf} \vspace{0.5cm}
\caption{(a) Time history of the turbulent kinetic energy $\mathcal{K}=\langle u'_i u'_i \rangle/2$ (black line) and enstrophy $\Omega$ (grey line), normalized by their mean values. (b) Normalized histogram of the streamwise (red) and shear (orange) components of the velocity fluctuations, $u'$ and $v'$. The lines and symbols are used to distinguish our results (lines) from those by \citet{pumir_1996a}.}
	\label{fig:pumir}
\end{figure}
The single-phase homogeneous shear turbulence has been validated by reproducing one of the cases investigated by \citet{pumir_1996a}; in particular, we simulated the Run No.~$2$ in that paper. The initial condition at $t = 0$ is a homogeneous isotropic turbulent field at $Re_\lambda = 50.8$, obtained in a square computational box of size $2\pi$ discretised with $256$ grid points in each direction. From the time history of the turbulent kinetic energy $\mathcal{K}$ and of the enstrophy $\Omega = \langle \omega_i \omega_i \rangle$, shown in \figref[a]{fig:pumir}, we observe a first transient phase for $0 \le t\mathcal{S} \le 30$, where the kinetic energy and enstrophy grow rapidly, followed by a statistically stationary state characterised by a cyclic succession of turbulent kinetic energy peaks rapidly followed by a peak in enstrophy with a time lag of approximately $5\mathcal{S}$. This behavior is well captured in our simulation. A quantitative validation is performed first by comparing the mean components of the velocity anisotropy tensor, $b_{ij}=\langle u_i u_j / u'_k u'_k - \delta_{ij}/3 \rangle$ computed in our simulations ($b_{11}=0.231$, $b_{22} = −0.129$, $b_{33} = −0.101$, $b_{12} = −0.147$) with the data reported by \citet{pumir_1996a}, and we found that the differences are below $5\%$. A further comparison is shown in \figref[b]{fig:pumir} where the normalized histograms of the streamwise and shear components of the velocity obtained with the present  simulations are compared with the results reported in the literature \citep{pumir_1996a}; again we observe a very good agreement.

@@

We start our analysis by considering the single-phase flow at $Re_z = 15200$. The problem is solved numerically on a computational mesh of $1312 \times 640 \times 624$ grid points and the simulation is run for approximately $250\mathcal{S}$ time units. Note that, the grid spacing is chosen sufficiently small for good resolution of the smallest turbulent scales as indicated by $\Delta x / \eta \approx 0.7$, where $\eta$ is the Kolmogorov scale defined as $\eta=\left( \mu/\rho \right)^{3/4}/\varepsilon^{1/4}$. The initial flow field is  fully developed single-phase homogeneous isotropic turbulence, and the mean shear $\mathcal{S}$ is applied from $t=0$. As shown in \figref[a]{fig:kin}, once the shear is applied, the flow undergoes an initial transient characterised by a strong increase in the production of turbulent kinetic energy, which is not in balance with the dissipation rate. After some time, however, the turbulent kinetic energy $\mathcal{K}$ decreases owing to an increase in the dissipation, reaching a new statistically steady state where, on average, the production balances the dissipation ($\mathcal{P} \approx \varepsilon$). This state, called steady-state shear turbulence, was first found and characterised by \cite{pumir_1996a} and later investigated by others \citep[e.g.][]{sekimoto_dong_jimenez_2016a}. The resulting Taylor microscale Reynolds number at the steady state is equal to $Re_\lambda \approx 145$ with the averaged spectrum of the TKE reported in \figref[b]{fig:kin}. Owing to the high Reynolds number, a clear $k^{-5/3}$ regime develops at intermediate scales. We also observe that the spectra of each individual component of the velocity are different at small wave numbers because of the large-scale anisotropy, while all spectra coincide at higher wave numbers, consistently with what observed by \cite{pumir_1996a}.

@@

\subsection{Size distribution}
We now study the transient and steady state property of the interface separating the two fluids. \figrefSC{fig:3dview} shows instantaneous snapshots of the two-phase flow at the statistically steady state, which is characterised by droplets with different sizes and shapes: in general we can observe that small droplets are approximately spherical, while the largest ones have very anisotropic shapes and show a preferential alignment with the direction of the mean shear. Also, as the Weber number decreases, the droplets size increases and larger droplets can sustain the spherical shape.

@@

\begin{figure}
	\centering
	\input{paper5/Cvol} \vspace{0.5cm} \\
\includegraphics[width=0.49\textwidth]{contL}
\put(-190,130){$(b)$}
\includegraphics[width=0.49\textwidth]{contR}
\put(-190,130){$(c)$}
	\caption{(a) Normalized cumulative volume distributions $\mathcal{V}/\mathcal{V}_\textrm{tot}$ of the dispersed phase at the steady state as a function of the equivalent spherical droplet diameters $D$. The horizontal grey line correspond to the level $\mathcal{V}=0.95\mathcal{V}_\textrm{tot}$. (b-c) Contour of the temporal evolution of the normalized cumulative volume distributions of the dispersed phase as a function  of the equivalent spherical droplet diameter for cases $4$ (b) and $5$ (c).}
	\label{fig:distr}
\end{figure}
Next, we aim to characterise the steady state size distribution of the emulsion. Thus, we first examine the cumulative volume, $\mathcal{V}$, as a function of the equivalent spherical diameter $D$ defined as the diameter of the sphere occupying the same volume, see \figref[a]{fig:distr}. Specifically, \figref[a]{fig:distr} shows the steady-state distributions of all cases, where each point on the curves represents the total volume of the droplets with equivalent diameter lower than $D$. In the figure, both $\mathcal{V}$ and $D$ are normalized by the global maximal values so that the curves are bounded uniformly from above by $1$. The figure shows that the cumulative volume distribution only has one inflection point ($d^2 \mathcal{V}/dD^2 = 0$), thus indicating that the probability density plot ($d \mathcal{V}/dD$) is single peaked. In \figref[a]{fig:distr} the Weber number $We_\lambda$ grows from right to left, as indicated by the list of symbols, suggesting that small droplets tend to be more common at high Weber numbers. Additionally, the range of the droplet diameters also narrows with increasing $We_\lambda$, since the cumulative volume grows faster to unity, as visually confirmed in \figrefS{fig:3dview}. Case $2$, blue line with circle, is the only simulation exhibiting a double peak (\ie $d \mathcal{V}/dD$ has two local maxima): this is due to the presence of very small droplets together with few large ones as can be seen in \figref[left]{fig:3dview}. Nevertheless, the overall trend of decreasing size for increasing Weber number is still consistent with the linear scaling between $\mathcal{N}_s$ and $We_\lambda$, as already observed in \figref[b]{fig:count}. The two bottom panels in \figrefS{fig:distr}, are contours of $\mathcal{V}/\mathcal{V}_\textrm{tot}$ as a function of the equivalent diameter $D$ and time, and can thus be interpreted as a cumulative spectrogram with most of the droplets centered in the region where the gradient of the color is the largest. In particular, we selected two specific cases, with same initial Weber number $We_0 \approx 2$, but different initial droplet size and surface tension, thus leading to different $We_\lambda$. The two figures show the transient behavior for cases $4$ and $5$, respectively: in \figref[b]{fig:distr} the mean size distribution remains relatively unchanged over time but it is subject to strong fluctuations, while \figref[c]{fig:distr} shows a clear shift of the population from large droplets to small ones, with a statistically steady state characterised by small fluctuations.

@@

\begin{figure}
	\centering
	\input{paper5/surf} \vspace{0.5cm}
	\caption{Total interfacial area $\mathcal{A}$ as a function of the Weber number $We_\lambda$. The grey solid line is a fit to our data in the form of $\mathcal{A} \propto We_\lambda^{1/3}$.}
	\label{fig:surf}
\end{figure}
Finally, we can further characterise the size distribution of the emulsion by inspecting the total surface area $\mathcal{A}$ of the dispersed phase. This quantity is very important when studying multiphase flows with interfaces, since the rate of work due to the surface tension is equal to the product of the surface tension coefficient and the rate of change in interfacial surface area \citep{dodd_ferrante_2016a}; also, for many industrial applications, the total surface area is often the most important parameter as surfactants tend to reside on the interface or it determines the chemical reaction rate. \figrefSC{fig:surf} reports the steady state surface area $\mathcal{A}$ as a function of the Weber number $We_\lambda$ and clearly shows that the surface area increases monotonically with the Weber number. As we have shown above that $\mathcal{N} \propto We_\lambda$, combining with mass conservation, \ie $\mathcal{N} D^3 \propto 1$, leads to the following relation for the total area: $\mathcal{A} \propto \mathcal{N} D^2 \propto We_\lambda^{1/3}$. In other words, the surface area of the droplets shall also increase with the Weber number defined by the Taylor length of the flow, with a slope of $1/3$. \figrefSC{fig:surf} verifies this scaling. We remark that in the derivation above, we have assumed that the droplets are spherical, which is not always true in our cases. However, provided the linear scaling between $\mathcal{N}$ and $We_\lambda$ remains valid, we expect the $1/3$ scaling law to hold for a wide range of emulsions.
